disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-10-30 article.Rnw
Tidy up and update MCMC results

More about mathematical details of Laplace approximation and automatic differentiation.

@@

%
<<installrun, echo=FALSE, message=FALSE>>=
#devtools::install_github("aknandi/disaggregation")
library(disaggregation, quietly = TRUE)
library(raster, quietly = TRUE)
library(dplyr, quietly = TRUE)
library(magrittr, quietly = TRUE)
@
%

%
<<installview, eval=FALSE>>=
devtools::install_github("aknandi/disaggregation")
library(disaggregation)
library(raster)
library(dplyr)
library(magrittr)
@
%

We then setup the data to use in the \pkg{disaggregation}.
%
<<setuppaths>>=
API_path <- 'data/api_subnational.csv'
population_path <-'data/pop_at_risk_pf_2013.tif'
shapefile_path <- 'data/admin2019_2.shp'

covariate_raster_paths <- c(
  'data/MODIS_LST_Day.mean.5km.tif',
  'data/MODIS_EVI.mean.5km.tif',
  'data/SRTM_elevation.5km.mean.tif',
  'data/MODIS_LST_Day.SD.5km.tif'
)

# Make a RasterStack of covariates to the extent of Madagascar and scale values
covariates <- lapply(covariate_raster_paths, raster)
covariate_stack <- stack(covariates)
covariate_stack <- crop(covariate_stack, extent(c(42, 52, -26, -10))) %>% scale

# Read in the incidence data and only select data from Madagascar 2013
api <- read.csv(API_path)
api <- api %>% filter(iso3 == 'MDG', year == 2013)

@@

%
\begin{table}
\begin{tabular}{l|ll|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (8 hours)} & \multicolumn{2}{|c|}{MCMC (24 seconds)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & sd & Mean & sd & Mean & sd \\
Intercept & -3.16 & 0.19 & -0.20 & 1.33 & -3.12 & 0.27 \\
Slope 1 & 0.32 & 0.23 & -0.27 & 0.80 & 0.24 & 0.27 \\
Slope 2 & 0.11 & 0.22 & -0.65 & 0.86 & 0.30 & 0.21\\
Slope 3 & -0.55 & 0.18 & -0.35 & 0.95 & -0.37 & 0.20 \\
Slope 4 & -0.23 & 0.16 & 0.12 & 0.35 & -0.24 & 0.21 \\
iid $log(\tau)$ & 1.06 & 0.26 & 0.04 & 1.16 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.29 & 0.61 & -0.87 & 0.94 & -3.55 & 0.59 \\
$log(\rho)$ & 0.75 & 0.34 & 0.65 & 0.93 & -0.56 & 0.30 \\
\end{tabular}
\end{table}
%

>>>>

@@

%
<<installrun, echo=FALSE, message=FALSE>>=
#devtools::install_github("aknandi/disaggregation")
library(disaggregation, quietly = TRUE)
@
%

%
<<installview, eval=FALSE>>=
devtools::install_github("aknandi/disaggregation")
library(disaggregation)
@
%

We then setup the data to use in the \pkg{disaggregation} package.

%
<<setuppaths>>=
library(raster)

API_path <- 'data/api_subnational.csv'
population_path <-'data/pop_at_risk_pf_2013.tif'
shapefile_path <- 'data/admin2019_2.shp'

covariate_raster_paths <- c(
  'data/MODIS_LST_Day.mean.5km.tif',
  'data/MODIS_EVI.mean.5km.tif',
  'data/SRTM_elevation.5km.mean.tif',
  'data/MODIS_LST_Day.SD.5km.tif')

# Make a RasterStack of covariates to the extent of Madagascar and scale values
covariates <- lapply(covariate_raster_paths, raster)
covariate_stack <- stack(covariates)
covariate_stack <- scale(crop(covariate_stack, extent(c(42, 52, -26, -10))))

# Read in the incidence data and only select data from Madagascar 2013
api <- read.csv(API_path)
api <- api[api$iso3 == 'MDG' & api$year == 2013, ]

@@

%
\begin{table}
\begin{tabular}{l|ll|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (8 hours)} & \multicolumn{2}{|c|}{MCMC (3 minutes)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & sd & Mean & sd & Mean & sd \\
Intercept & -3.07 & 0.37 & -3.31 & 0.19 & -3.12 & 0.27 \\
Slope 1 & 0.22 & 0.27 & 0.50 & 0.43 & 0.24 & 0.27 \\
Slope 2 & 0.30 & 0.20 & 0.21 & 0.42 & 0.30 & 0.21\\
Slope 3 & -0.35 & 0.21 & -0.50 & 0.33 & -0.37 & 0.20 \\
Slope 4 & -0.22 & 0.21 & -0.24 & 0.15 & -0.24 & 0.21 \\
iid $log(\tau)$ & 1.06 & 0.26 & -0.14 & 1.13 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.29 & 0.61 & -3.37 & 2.35 & -3.55 & 0.59 \\
$log(\rho)$ & 0.75 & 0.34 & 2.78 & 1.72 & -0.56 & 0.30 \\
\end{tabular}
\end{table}
%
